Advancements in Moltres for Time-Dependent Multiphysics Molten Salt Reactor Modeling

### 2024-12-09 presentation/3d.tex
slide edits
presentation edits

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: 3-D Neutronics Eigenvalue Simulations}
  \begin{columns}
    \column{5.5cm}
  \textbf{3-D Full-Core MSRE Model}
  \begin{figure}[p]
    \centering
    \includegraphics[width=0.85\columnwidth]{msre-picture}
    \caption{Vertical cross section of the actual \gls{MSRE} vessel.}
    \label{fig:msre-picture}
  \end{figure}
    \column{6cm}
  \begin{figure}[p]
    \centering
    \includegraphics[width=.95\columnwidth]{msre-geom-vert}
    \caption{Vertical cross section of the 3-D numerical \gls{MSRE} model offset by 5.08 cm to show
    the control rod thimble and homogenized sample basket.}
    \label{fig:msre-geom-vert}
  \end{figure}
\end{columns}
\end{frame}

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: 3-D Neutronics Eigenvalue Simulations}
  \textbf{3-D Full-Core MSRE Model Details}
  \begin{itemize}
    \item Hybrid $S_6$-diffusion method
    \item $^{235}$U concentration at initial criticality
    \item Uniform temperature at 911 K
    \item Stabilization factor of $c=250$
    \item Void constant of $\varsigma=0.5$
    \item Uncorrected diffusion coefficient values capped at $D_g = 2.5$
  \end{itemize}
  \vspace{.2cm}

  These parameters are required for numerical stability in the air-filled control rod
  thimble region.
  \vspace{.2cm}

  All hybrid method results are compared with MSRE experimental data, the MSRE numerical benchmark
  report data (Serpent 2 model) \cite{fratoni_molten_2020}, and the OpenMC model in this work.
\end{frame}

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: 3-D Neutronics Eigenvalue Simulations}
  \textbf{MSRE at Initial Criticality}
  \begin{table}[htb]
    \centering
    \caption{$k_\text{eff}$ values from \gls{MSRE} experimental data, the \gls{MSRE} numerical
    benchmark \cite{fratoni_molten_2020}, and the OpenMC and Moltres models in this work.}
    \begin{tabular}{l S[table-format=1.5(2)]}
      \toprule
       & {$k_\text{eff}$} \\
       \midrule
      \gls{MSRE} experimental data & 1.00000(420) \\
      Serpent 2 (Numerical benchmark) & 1.02132(3) \\
      OpenMC (This work) & 1.01308(20) \\
      Hybrid (This work) & 1.01955 \\
      Diffusion (This work) & 1.01885 \\
      \bottomrule
    \end{tabular}
    \label{table:initial-crit}
  \end{table}

  \begin{itemize}
    \item The Serpent 2 benchmark model reports a $k_\text{eff}$ of 1.01093(3) after considering some
      of the geometrical modifications used in the OpenMC model.
    \item The hybrid and neutron diffusion models agree with the OpenMC model within 700 pcm.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: 3-D Neutronics Eigenvalue Simulations}
  \textbf{MSRE Rod Worth Measurements}
  \begin{figure}[t]
    \centering
    \includegraphics[width=0.8\columnwidth]{rod-worth-curve}
    \caption{Reactivity inserted by Rod 1 at various rod positions relative to the full insertion.}
    \label{fig:rod-worth}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: 3-D Neutronics Eigenvalue Simulations}
  \textbf{MSRE Rod Worth Measurements}
  \begin{table}[t]
    \centering
    \caption{Total rod worth of Rod 1 when fully inserted.}
    \begin{tabular}{l S[table-format=4(2)] S}
      \toprule
       & {$\rho_\text{worth}$ [pcm]} & {Percentage discrepancy [\%]}\\
       \cmidrule(rl){2-2} \cmidrule(l){3-3}
      \gls{MSRE} experimental data & 2250(67) & {-}\\
      OpenMC (This work) & 2364(44) & 5.1 \\
      Hybrid (This work) & 2345 & 4.2 \\
      Diffusion (This work) & 2725 & 21.1 \\
      \bottomrule
    \end{tabular}
    \label{table:rod-worth}
  \end{table}
  \vspace{.2cm}

@@

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: 3-D Neutronics Eigenvalue Simulations}
  \textbf{Computational Performance}
  \begin{itemize}
    \item All simulations ran on the Polaris supercomputer system at Argonne National Laboratory.
    \item Each 3-D full-core simulation consisted of 750M and 1.69B degrees of freedom for the
      neutron diffusion and $S_N$ subsolvers, respectively.
    \item 3-D full-core simulations required at least 40 compute nodes with 512 GB RAM each due to
      strict memory requirements (significant improvements in memory use is possible) and took 2.2
      h to complete.
    \item The hybrid method took about four times longer than the neutron diffusion method.
    \item 30 \% of compute time spent on data transfers between the neutron diffusion and $S_N$
      subsolvers (Reduced to 18 \% in subsequent simulations after optimizations)
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: 3-D Neutronics Eigenvalue Simulations}
  \textbf{Strong Scaling Test}
  \vspace{.2cm}

  Performed a strong scaling test on the 3-D quarter-core MSRE model on 10, 20, 40, and 80 compute
  nodes. The $S_N$ and diffusion subsolvers scale well throughout the test.
  The $S_N$-diffusion data transfer processes scale poorly beyond 40 nodes.
  \begin{figure}[t]
    \centering
    \begin{subfigure}[b]{0.32\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{scaling-total}
      \caption{Total wall time}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{scaling-solver}
      \caption{Solver wall time}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{scaling-transfer}
      \caption{Transfer wall time}
    \end{subfigure}
    \caption{The total, solver, and transfer wall time of hybrid method simulations of the 3-D
    quarter-core model on 10, 20, 40, and 80 compute nodes (32 processors per node) of the Polaris
    supercomputer. All axes are in log scale.}
    \label{fig:scaling}
  \end{figure}
\end{frame}

>>>>

\begin{frame}
  \frametitle{3-D MSRE Full-Core Model}
  \begin{columns}
    \column{5.5cm}
  \begin{figure}[p]
    \centering
    \includegraphics[width=0.8\columnwidth]{msre-picture}
    \caption{Vertical cross section of the actual \gls{MSRE} vessel.}
    \label{fig:msre-picture}
  \end{figure}
    \column{6cm}
  \begin{figure}[p]
    \centering
    \includegraphics[width=.87\columnwidth]{msre-geom-vert}
    \caption{Vertical cross section of the 3-D numerical \gls{MSRE} model offset by 5.08 cm to show
    the control rod thimble and homogenized sample basket.}
    \label{fig:msre-geom-vert}
  \end{figure}
\end{columns}
\end{frame}

\begin{frame}
  \frametitle{3-D MSRE Neutronics Modeling Approach}
  \begin{columns}
    \column{5.5cm}
    \textbf{3-D Full-Core MSRE Model Details}
    \begin{itemize}
      \item Hybrid $S_6$-diffusion method
      \item Eight neutron energy groups
      \item $^{235}$U concentration at initial criticality
      \item Uniform temperature at 911 K
    \end{itemize}
    \vspace{.2cm}

    All hybrid method results are compared with MSRE experimental data, the MSRE numerical benchmark
    report data (Serpent 2 model) \cite{fratoni_molten_2020}, and the OpenMC model in this work.
    \column{5.5cm}
    \begin{figure}[p]
      \centering
      \includegraphics[width=.9\columnwidth]{wedge-view-high-res.png}
      \caption{3-D section view of the 3-D numerical \gls{MSRE} model showing
      the three control rod thimbles and the fuel-graphite lattice.}
      \label{fig:msre-geom-vert}
    \end{figure}
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{3-D MSRE Neutronics Simulation Results}
  \textbf{MSRE at Initial Criticality}
  \begin{table}[htb]
    \centering
    \caption{$k_\text{eff}$ values from \gls{MSRE} experimental data, the \gls{MSRE} numerical
    benchmark \cite{fratoni_molten_2020}, and the OpenMC and Moltres models in this work.}
    \begin{tabular}{l S[table-format=1.5(2)]}
      \toprule
      Source & {$k_\text{eff}$} \\
       \midrule
      \gls{MSRE} experimental data & 1.00000(420) \\
      Serpent 2 (Numerical benchmark) & 1.02132(3) \\
      OpenMC (This work) & 1.01308(20) \\
      Hybrid (This work) & 1.01957 \\
      Diffusion (This work) & 1.01885 \\
      \bottomrule
    \end{tabular}
    \label{table:initial-crit}
  \end{table}
  \vspace{.2cm}

  $\Rightarrow$ The hybrid and neutron diffusion models agree with the Serpent 2 and OpenMC models within
  700 pcm.
\end{frame}

\begin{frame}
  \frametitle{3-D MSRE Neutronics Simulation Results}
  \textbf{MSRE Rod Worth Measurements}
  \begin{figure}[t]
    \centering
    \includegraphics[width=0.75\columnwidth]{rod-worth-curve}
    \caption{Reactivity inserted by Rod 1 at various rod positions relative to the full insertion.}
    \label{fig:rod-worth}
  \end{figure}
\end{frame}

\begin{frame}
  \frametitle{3-D MSRE Neutronics Simulation Results}
  \textbf{MSRE Rod Worth Measurements}
  \begin{table}[t]
    \centering
    \caption{Total rod worth of Rod 1 when fully inserted.}
    \small
    \begin{tabular}{l S[table-format=4(2)] S}
      \toprule
       & {$\rho_\text{worth}$ [pcm]} & {Percentage discrepancy [\%]}\\
       \cmidrule(rl){2-2} \cmidrule(l){3-3}
      \gls{MSRE} experimental data & 2250(67) & {-}\\
      OpenMC (This work) & 2364(44) & 5.1 \\
      Hybrid (This work) & 2345 & 4.2 \\
      Diffusion (This work) & 2725 & 21.1 \\
      \bottomrule
    \end{tabular}
    \label{table:rod-worth}
  \end{table}
  \vspace{.2cm}

@@

\begin{frame}
  \frametitle{3-D MSRE Neutronics Simulation Results}
  \textbf{Computational Performance}
  \begin{itemize}
    \item All simulations ran on the Polaris supercomputer system at Argonne National Laboratory.
    \item Each 3-D full-core simulation consisted of 750M and 1.69B degrees of freedom for the
      neutron diffusion and $S_N$ subsolvers, respectively.
    \item 3-D full-core simulations required at least 40 compute nodes with 512 GB RAM each due to
      strict memory requirements (significant improvements in memory use is possible) and took 2.2
      h to complete.
    \item The hybrid method took about four times longer than the neutron diffusion method.
    \item 30 \% of compute time spent on data transfers between the neutron diffusion and $S_N$
      subsolvers (Reduced to 18 \% in subsequent simulations after optimizations)
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{3-D MSRE Neutronics Simulation Results}
  \textbf{Strong Scaling Test}
  \vspace{.2cm}

  Performed a strong scaling test on the 3-D quarter-core MSRE model on 10, 20, 40, and 80 compute
  nodes. The $S_N$ and diffusion subsolvers scale well throughout the test.
  The $S_N$-diffusion data transfer processes scale poorly beyond 40 nodes.
  \begin{columns}
  \column{11cm}
  \begin{figure}[t]
    \centering
    \begin{subfigure}[b]{0.32\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{scaling-total}
      \caption{Total wall time}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{scaling-solver}
      \caption{Solver wall time}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\columnwidth}
      \centering
      \includegraphics[width=\columnwidth]{scaling-transfer}
      \caption{Transfer wall time}
    \end{subfigure}
    \caption{The total, solver, and transfer wall time of hybrid method simulations of the 3-D
    quarter-core model on 10, 20, 40, and 80 compute nodes (32 processors per node) of the Polaris
    supercomputer. All axes are in log scale.}
    \label{fig:scaling}
  \end{figure}
\end{columns}
\end{frame}

### 2024-12-09 presentation/conclusion.tex
slide edits
presentation edits

\begin{frame}
  \frametitle{Conclusion}
  \begin{block}{\textbf{Moltres Multiphysics V\&V Studies}}
    \textbf{Relevance}
    \begin{itemize}
      \item Existing multiphysics coupling capabilities in Moltres must be verified and validated
    \end{itemize}
    \textbf{Results Presented}
    \begin{itemize}
      \item CNRS numerical benchmark study with Moltres
      \item MSRE pump transient V\&V study with Moltres
    \end{itemize}
    \textbf{Major takeaways}
    \begin{itemize}
      \item Moltres is highly consistent with other MSR simulation tools in accurately modeling:
      \begin{itemize}
        \item Salt flow-induced temperature and DNP drift
        \item Temperature ractivity feedback due to Doppler broadening and thermal expansion
        \item Buoyancy-driven flow due to temperature gradients
        \item Time-varying and looped precursor flow
      \end{itemize}
    \end{itemize}
  \end{block}
\end{frame}

@@

\begin{frame}
  \frametitle{Conclusion}
  \begin{block}{\textbf{Hybrid $S_N$-Diffusion Method}}
    \textbf{Relevance}
    \begin{itemize}
      \item No MSR studies exist for time-dependent MSR simulations involving reactivity-initiated
        transients using control rods
    \end{itemize}
    \textbf{Results Presented}
    \begin{itemize}
      \item Development and implementation of a hybrid $S_N$-diffusion method for
        accurate control rod modeling in Moltres
      \item Verification, validation, and demonstration of the hybrid $S_N$-diffusion
        method through 1-D, 2-D, \& 3-D analyses of the MSRE
    \end{itemize}
    \textbf{Major Takeaways}
    \begin{itemize}
      \item The hybrid method is an iterative method that applies a $S_N$ subsolver around control
        rod regions for improved rod worth estimates
      \item The hybrid method applies an adaptive domain decomposition technique to
        couple the $S_N$ subsolver and the neutron diffusion solver
      \item The hybrid method accurately reproduces control rod worths at only four times the
        computational cost of the neutron diffusion method
      \item The hybrid method exhibits decent scalability on high-performance computing clusters
    \end{itemize}
  \end{block}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Conclusion}
  \begin{block}{\textbf{Moltres Multiphysics V\&V Studies}}
    \textbf{Relevance}
    \begin{itemize}
      \item Existing multiphysics coupling capabilities in Moltres must be verified and validated
    \end{itemize}
    \textbf{Results Presented}
    \begin{itemize}
      \item CNRS numerical benchmark study with Moltres (Dissertation)
      \item MSRE pump transient V\&V study with Moltres
    \end{itemize}
    \textbf{Major takeaways}
    \begin{itemize}
      \item Moltres is highly consistent with other MSR simulation tools in accurately modeling:
      \begin{itemize}
        \item Salt flow-induced temperature and DNP drift
        \item Temperature ractivity feedback due to Doppler broadening and thermal expansion
        \item Buoyancy-driven flow due to temperature gradients
        \item Time-varying and looped precursor flow
      \end{itemize}
    \end{itemize}
  \end{block}
\end{frame}

@@

\begin{frame}
  \frametitle{Conclusion}
  \begin{block}{\textbf{Hybrid $\bm{S_N}$-Diffusion Method}}
    \textbf{Relevance}
    \begin{itemize}
      \item There are no MSR simulation tools or studies that explicitly model moving control rods.
    \end{itemize}
    \textbf{Results Presented}
    \begin{itemize}
      \item Development and implementation of a hybrid $S_N$-diffusion method for
        accurate control rod modeling in Moltres
      \item Verification, validation, and demonstration of the hybrid $S_N$-diffusion
        method through 1-D, 2-D, \& 3-D analyses of the MSRE
    \end{itemize}
    \textbf{Major Takeaways}
    \begin{itemize}
      \item The hybrid method is an iterative method that applies a $S_N$ subsolver around control
        rod regions for improved rod worth estimates
      \item The hybrid method applies an adaptive boundary coupling between
        the $S_N$ subsolver and the neutron diffusion solver to smooth flux gradients
      \item The hybrid method accurately reproduces control rod worths at only four times the
        computational cost of the neutron diffusion method
      \item The hybrid method exhibits good scalability on high-performance computing clusters
    \end{itemize}
  \end{block}
\end{frame}

### 2024-12-09 presentation/control-rod.tex
presentation edits

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: Motivation}
  \begin{columns}
    \hfill
    \column[t]{5cm}
    \textbf{Control Rods in MSRs}
    \vspace{.2cm}
    \begin{figure}
      \centering
      \includegraphics[width=\columnwidth]{images/msre-cutout}
      \caption{\footnotesize MSRE reactor vessel \cite{robertson_msre_1965}}
    \end{figure}
    \hfill
    \column[t]{6cm}
    \begin{figure}
      \centering
      \includegraphics[width=.8\columnwidth]{images/tmsr}
      \caption{\footnotesize Cross-sectional views of the TMSR-LF1
      \cite{liu_sensitivityuncertainty_2020}}
    \end{figure}
    \begin{figure}
      \centering
      \includegraphics[width=.5\columnwidth]{images/tap-msr-rods}
      \caption{\footnotesize Cross-sectional view of the TAP MSR \cite{lee_neutronics_2020}}
    \end{figure}
    \hfill
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: Motivation}
  \textbf{Control rods provide a means of controlling the fission rate in nuclear reactors.} 
  \begin{itemize}
    \item Facilitate reactor start-up, shut-down, or load-following operations
    \item Consist of highly neutron-absorbing materials such as boron or gadolinium
  \end{itemize}
  \textbf{MSRs contain comparatively fewer control rods than most other reactor types due to:}
  \begin{itemize}
    \item Uniform liquid fuel burnup
    \item Strong passive safety of the liquid fuel form
    \item Low excess reactivity of fuel inventory
    \item Availability of other control mechanisms
  \end{itemize}
  \pause
  \textbf{Nevertheless, it is important to characterize control rod effects in all relevant
  transient scenarios.}
\end{frame}

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: Motivation}
  \textbf{Control rods induce highly anisotropic neutron fluxes and steep flux gradients in their
  vicinity.}
  \begin{block}{\textbf{The Control Rod Modeling Dilemma}}
    \begin{itemize}
      \item Neutron diffusion, $P_1$, and $SP_N$ methods perform poorly near control rod regions
        due to the highly anisotropic neutron fluxes and steep flux gradients
      \item High-fidelity neutron transport methods remain too computationally expensive for
        routine time-dependent multiphysics simulations
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}
  \frametitle{Hybrid $S_N$-Diffusion Method: Motivation}
  \textbf{Control Rod Modeling in MSR Multiphysics Studies}
  \vspace{.2cm}

  Common simplifications applied to control rod modeling include:
  \begin{itemize}
    \item Homogenized, coarse-mesh geometries containing static control rods with albedo neutron
      flux boundary conditions \cite{kophazi_development_2009} or transport-corrected cross
      sections \cite{cui_development_2021, jaradat_development_2021, yang_development_2022}
      \begin{itemize}
        \item Neutronics mesh differs from thermal-hydraulics mesh
        \item 1-D thermal-hydraulics model with uniform or prescribed heat deposition
        \item Static calibration factors may not be suitable for time-dependent simulations
      \end{itemize}
    \item Scaling the neutron source term to simulate moving control rods
      \cite{delpech_benchmark_2003, krepel_dyn3d-msr_2007, jaradat_development_2021,
      yang_development_2022}
      \begin{itemize}
        \item Does not capture local or asymmetric flux changes
      \end{itemize}
  \end{itemize}

  \begin{block}{\textbf{Technical Gap}}
    \textbf{There are no existing MSR simulation tools or studies involving moving control rods
    which are explicitly modeled.}
  \end{block}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Control Rods in MSRs}
  \begin{columns}
    \hfill
    \column[t]{5cm}
    \vspace{.2cm}
    \begin{figure}
      \centering
      \includegraphics[width=\columnwidth]{images/msre-cutout}
      \caption{\footnotesize MSRE reactor vessel \cite{robertson_msre_1965}}
    \end{figure}
    \hfill
    \column[t]{6cm}
    \begin{figure}
      \centering
      \includegraphics[width=.8\columnwidth]{images/tmsr}
      \caption{\footnotesize Cross-sectional views of the TMSR-LF1
      \cite{liu_sensitivityuncertainty_2020}}
    \end{figure}
    \begin{figure}
      \centering
      \includegraphics[width=.5\columnwidth]{images/tap-msr-rods}
      \caption{\footnotesize Cross-sectional view of the TAP MSR \cite{lee_neutronics_2020}}
    \end{figure}
    \hfill
  \end{columns}
\end{frame}

\begin{frame}
  \frametitle{Control Rods in MSRs}
  \textbf{Control rods provide a means of controlling the fission rate in nuclear reactors.} 
  \begin{itemize}
    \item Facilitate reactor start-up, shut-down, or load-following operations
    \item Consist of highly neutron-absorbing materials such as boron or gadolinium
  \end{itemize}
  \textbf{Control rods are also important for licensing and safety characterization.}

  $\Rightarrow$ \textbf{It is important to characterize control rod effects in all relevant
  transient scenarios.}
%  \textbf{Many MSR designs contain comparatively fewer control rods than most other reactor types due to:}
%  \begin{itemize}
%    \item Uniform liquid fuel burnup
%    \item Strong passive safety of the liquid fuel form
%    \item Low excess reactivity of fuel inventory
%    \item Availability of other control mechanisms
%  \end{itemize}

\end{frame}

\begin{frame}
  \frametitle{Control Rod Modeling}
  \textbf{Control rods induce highly anisotropic neutron fluxes and steep flux gradients in their
  vicinity.}
  \begin{block}{\textbf{The Control Rod Modeling Dilemma}}
    \begin{itemize}
      \item Neutron diffusion, $P_1$, and $SP_N$ methods perform poorly near control rod regions
        due to the highly anisotropic neutron fluxes and steep flux gradients
      \item High-fidelity neutron transport methods remain too computationally expensive for
        routine time-dependent multiphysics simulations
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}
  \frametitle{Control Rod Modeling in MSR Multiphysics Studies}
  \vspace{.2cm}

  Common approximations applied to control rod modeling include:
  \begin{itemize}
    \item Homogenized, coarse-mesh geometries containing static control rods with albedo neutron
      flux boundary conditions \cite{kophazi_development_2009} or transport-corrected cross
      sections \cite{cui_development_2021, jaradat_development_2021, yang_development_2022}
      \begin{itemize}
        \item Neutronics geometry differs from thermal-hydraulics geometry
        \item Static calibration factors may not be suitable for time-dependent simulations
      \end{itemize}
    \item Scaling the neutron source term to simulate moving control rods
      \cite{delpech_benchmark_2003, krepel_dyn3d-msr_2007, jaradat_development_2021,
      yang_development_2022}
      \begin{itemize}
        \item Does not capture local or asymmetric flux changes
      \end{itemize}
  \end{itemize}

  \begin{block}{\textbf{Technical Gap}}
    \textbf{There are no MSR simulation tools or studies that explicitly model moving control rods.}
  \end{block}
\end{frame}

### 2024-12-09 presentation/msr.tex
presentation edits

\begin{frame}
  \frametitle{What is a Molten Salt Reactor (MSR)?}
	\begin{itemize}
	  \item Advanced nuclear reactor fueled by fissile
		material dissolved in a molten salt mixture
	  \item In most MSR designs, the fuel salt mixture doubles as the primary coolant for the
        reactor
	  \item Both thermal- and fast-spectrum configurations are viable
	\end{itemize}
	\begin{figure}
	  \centering
	  \includegraphics[width=.5\textwidth]{./images/msr}
      \caption{Schematic diagram of a general channel-type MSR concept
      \cite{u.s._doe_nuclear_energy_research_advisory_committee_technology_2002}.}
	  \label{fig:msr}
	\end{figure}
\end{frame}

%\begin{frame}
%  \frametitle{What is a Molten Salt Reactor (MSR)?}
%  \textbf{Advantages of MSRs over other reactor types}
%  \begin{itemize}
%    \item Robust passive safety
%      \begin{itemize}
%        \item strong temperature feedback
%        \item large thermal margin to boiling
%      \end{itemize}
%    \item Freeze plug drains fuel salt into containment tanks under emergency situations
%    \item Online refueling and reprocessing can:
%      \begin{itemize}
%        \item reduce reactor downtime
%        \item reduce required fissile inventory in reactor at any given time
%        \item reduce transuranic waste produced
%        \item allow for $^{233}$U breeding from $^{232}$Th
%      \end{itemize}
%    \item Viable as fast-spectrum breeder/burner reactor
%    \item Can provide high-temperature heat for industrial heat applications
%  \end{itemize}
%\end{frame}

\begin{frame}
  \frametitle{Molten Salt Reactor Modeling \& Simulation}
  \textbf{While modeling MSRs is not necessarily more difficult than modeling solid-fueled
  reactors, we must adapt our software tools to accurately model phenomena unique to MSRs.}\\

  \textbf{Phenomena which pose challenges for MSR modeling}
  \begin{itemize}
	\item Strong multiphysics interactions involving neutron flux, temperature, and flow in the
      reactor core
	  \begin{itemize}
		\item Strong temperature feedback due to thermal expansion of liquid fuel salt
		\item Movement of \gls{DNP} along primary coolant loop
        \item Advection-dominated heat transfer
	  \end{itemize}
    \item Loss of delayed neutrons to out-of-core decay
    \item Complex turbulent flow effects in MSRs
  \end{itemize}
\end{frame}

>>>>

%\begin{frame}
%  \frametitle{What is a Molten Salt Reactor (MSR)?}
%	\begin{itemize}
%	  \item Advanced nuclear reactor fueled by fissile
%		material dissolved in a molten salt mixture
%	  \item In most MSR designs, the fuel salt mixture doubles as the primary coolant for the
%        reactor
%	  \item Both thermal- and fast-spectrum configurations are viable
%	\end{itemize}
%	\begin{figure}
%	  \centering
%	  \includegraphics[width=.5\textwidth]{./images/msr}
%      \caption{Schematic diagram of a general channel-type MSR concept
%      \cite{u.s._doe_nuclear_energy_research_advisory_committee_technology_2002}.}
%	  \label{fig:msr}
%	\end{figure}
%\end{frame}

\begin{frame}
  \frametitle{Molten Salt Reactor Modeling \& Simulation}
  \textbf{What is a Molten Salt Reactor (MSR)?}
  \begin{itemize}
	\item MSRs are advanced nuclear reactor fueled by fissile
	  material dissolved in a molten salt mixture.
    \item While modeling MSRs is not necessarily more difficult than modeling solid-fueled
      reactors, we must adapt our software tools to accurately model phenomena unique to MSRs.
  \end{itemize}

  \textbf{Phenomena that pose challenges for MSR modeling}
  \begin{itemize}
	\item Strong multiphysics interactions involving neutron flux, temperature, and flow in the
      reactor core
	  \begin{itemize}
		\item Strong temperature feedback due to thermal expansion of liquid fuel salt
		\item Movement of \glspl{DNP} along primary coolant loop
        \item Advection-dominated heat transfer
	  \end{itemize}
    \item Loss of delayed neutrons to out-of-core decay
    \item Complex turbulent flow effects in MSRs
  \end{itemize}
\end{frame}
